\documentclass{exam}
\usepackage{longtable}

% Bibliographic elements
\title{DATA3304 Quiz 1}
\date{\today}
\author{Bow Valley College\\Data Management and Analytics}

% Header
\pagestyle{headandfoot}
\firstpageheader{DATA3304}{Quiz 1}{February 16, 2024}
\firstpageheadrule
\runningheader{DATA3304}{Quiz 1}{February 16, 2024}
\runningheadrule

\begin{document}
Name:\enspace\hrulefill
\begin{questions}

    \question For each of the two scenarios identify whether the rows of the example data
    are a statistically independent sample, or if the rows are dependent on each other.
    Please provide a one or two sentence explanation.
    \begin{parts}
        \part A commercial vehicle servicing company runs a large maintenance shop with a
        complex multistage workflow. A mechanic can only service one vehicle at a time. The
        vehicles are not moved, so only one service bay can hold a vehicle at a time. The
        quality control on the maintenance requires that only one mechanic can service a
        vehicle at a time. You have been given a dataset to determine bottlenecks in service
        process.
        \begin{longtable}{llllll}
            Vehicle & Bay & Mechanic & Start & Stop & $\cdots$\\
            \hline
            \endhead
            10 & 3 & A & 8 & 12 & $\cdots$\\
            10 & 3 & B & 13 & 17 & $\cdots$\\
            20 & 7 & C & 9 & 11 & $\cdots$\\
            20 & 7 & A & 13 & 15 & $\cdots$\\
            \vdots & \vdots & \vdots & \vdots & \vdots & $\ddots$
        \end{longtable}
        \vspace{\stretch{1}}
        \part A biologist is testing a new growth enzyme for fruit bearing plants. The
        biologist has carefully designed a controlled experiment of the effect of the
        soil concentration of the enzyme, ensuring all other conditions are held constant
        across all the plants, and each plant was isolated. At the end of the study the
        total mass of fruit produced was measured.
        \begin{longtable}{llll}
            Plant & Soil Concentration & Fruit Mass & $\cdots$\\
            \hline
            1 & 0.5 & 4 & $\cdots$\\
            2 & 1 & 10 & $\cdots$\\
            3 & 2 & 12 & $\cdots$\\
            \vdots & \vdots & \vdots & $\ddots$
            \endhead
        \end{longtable}
        \vspace{\stretch{1}}
    \end{parts}

    \newpage
    \question The analysts at a shipping company estimate mileage costs in dollars (\$) with
    a simple linear equation $f(X) = Y + r \cdot X$, where $X$ is the mileage measured in
    total kilometers traveled by the shipping vehicles, and $Y$ is the constant cost of
    operation.

    Using reports from their tracking database the constant cost $Y$ was stated as
    \$7639.37. However, the constant cost reimbursement system only pays out in multiples of
    \$100 dollars. The total mileage $X$ was reported as 479456 km, but the odometer
    tracking only has a resolution of 10 km.
    \begin{parts}
        \part Using rounding at half away from zero please round each measurement to the
        reliable digits, and using the standard notation from class provide the absolute
        uncertainty of the constant cost and the total mileage.
        \vspace{\stretch{1}}
        \part Assuming the company has set the value of the rate constant $r$ as 125, what
        are the units of measurement of $r$, and what is the absolute uncertainty in the
        total mileage cost $f(X)$.
        \vspace{\stretch{1}}
    \end{parts}

    \newpage
    \question A service company is planning to implement random drug screening of their site
    workers. Currently only 3 in 100 Albertans use illicit stimulants. Please use the outlined
    drug screening Confusion Matrix in your answer.
    \begin{longtable}{lp{3cm}p{3cm}}
        & \multicolumn{2}{c}{Actual Substance Use} \\
        Test Result & Absent & Present\\
        \hline
        \endhead\\
        Positive & $3/20$ \par False Positive & $19/20$ \par True Positive\\\\
        Negative & $17/20$ \par True Negative & $1/20$ \par False Negative
    \end{longtable}
    \begin{parts}
        \part If a worker tests positive what is the incorrect conclusion reached by the
        Prosecutor's Fallacy, please specify either of the incorrect probabilities from the
        confusion matrix.
        \vspace{\stretch{1}}
        \part What is the correct conclusion and probability of having used illicit
        stimulants, please show your work.
        \vspace{\stretch{1}}
    \end{parts}
\end{questions}
\end{document}